New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/schur.tex
tableaux abbot

This shows the inequality \(S(2+2) \geqslant S^+(3)S(2)\), with the extra constant. 
We prooved \(S^+(3) = 9\).The special color is blue.

\(\overset{SF\textrm{-template}}{\textrm{Sum-free partition} \left \updownarrow\overleftrightarrow{\begin{tabular}{|*{9}{c|}}
	\hline
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
	\hline
	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{red} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
	\hline
	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{red} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
	\hline
	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{red} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36\\
	\hline
	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 & & & & &\\
	\hline
\end{tabular}}
\right.}\)
 \\

\begin{center}
\(SF\)-template with 3 colors (it is actually maximal)\\
\begin{tabular}{|*{9}{c|}}
	\hline 
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
	\hline
\end{tabular} \\

Sum-free partition (\(S(2)\) actually) \\
\begin{tabular}{|*{4}{c|}}
	\hline 
	\cellcolor{blue} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{blue} 4 \\
	\hline
\end{tabular}
\end{center}

@@

\[ f : [\![1,p]\!] \longrightarrow [\![1,k+1]\!] \text{ and } \forall (x,y) \in [\![1,p]\!]^2, \left\{
\begin{array}{ll}
	f(x) = f(y) \leqslant k \\
	x + y > p
\end{array}
\right.
\Longrightarrow f(x+y-p) \neq f(x)
\]
with also the sum-free condition : \[ \forall (x,y) \in [\![1,p]\!]^2 \text{, } f(x) = f(y)
\Longrightarrow f(x+y) \neq f(x) \]

@@

We now define \(h : [\![1,pq]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
\( \forall x \in [\![1,pq + m_{k+1}-1]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q]\!] \) and \( u \in
[\![0,p-1]\!] \).
This decomposition if of course unique. If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1)\) \(h(x) = k + g(\alpha) \).
Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.

Let \(x,y \in [\![1,pq]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq\). We write \(x = \alpha p - u\) and \(y =
\beta p - v\). \\
We simply need \(h(x+y) \neq h(x)\). \\

>>>>

This shows the inequality \(S(2+2) \geqslant S^+(3)S(2) + 4\). The special color is blue and is first used
to color 5, hence \(4 = m_{3} - 1\). 
We prooved \(S^+(3) = 9\). The special color is blue.

\begin{center}
\(\overset{S^+(3)}{\left. \overleftrightarrow{\begin{tabular}{|*{9}{c|}}
	\hline
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
	\hline
	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{red} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
	\hline
	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{red} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
	\hline
	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{red} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36\\
	\hline
	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 & & & & &\\
	\hline
\end{tabular}}
\right \updownarrow S(2)}\)
\end{center}

\begin{center}
\(S^+(3)\)\\
\begin{tabular}{|*{9}{c|}}
	\hline 
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
	\hline
\end{tabular} \\

\(S(2)\) \\
\begin{tabular}{|*{4}{c|}}
	\hline 
	\cellcolor{blue} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{blue} 4 \\
	\hline
\end{tabular}
\end{center}

@@

\[ f : [\![1,p]\!] \longrightarrow [\![1,k+1]\!] \text{ and } \forall (x,y) \in [\![1,p]\!]^2, \left\{
\begin{array}{ll}
	f(x) = f(y) \leqslant k \\
	x + y > p
\end{array}
\right.
\Longrightarrow f(x+y-p) \neq f(x)
\]
with also the sum-free condition : \[ \forall (x,y) \in [\![1,p]\!]^2 \text{, } f(x) = f(y)
\Longrightarrow f(x+y) \neq f(x) \]
Moreover, by definition of \(m_{k+1}\), if \(x < m_{k+1}\), \(f(x) \leqslant k\).

@@

We now define \(h : [\![1,pq+m_{k+1}-1]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
\( \forall x \in [\![1,pq + m_{k+1}-1]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q+1]\!] \) and \( u \in
[\![0,p-1]\!] \).
This decomposition if of course unique. \\
If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1)\) \(h(x) = k + g(\alpha) \). \\
If \(\alpha = q+1\), we have a problem plugging it into \(g\). Hopefully, this issue never arises : if 
\(\alpha = q+1\), we have \(u > p - m_{k+1}\) since \(x \in [\![1,pq + m_{k+1}-1]\!]\), hence \(p-u < m_{k+1}\) and \(f(p-u) \leqslant k\). \\
Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.

Let \(x,y \in [\![1,pq + m_{k+1}-1]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq+m_{k+1}-1\). We write \(x = \alpha p - u\) and \(y =
\beta p - v\). \\
We simply need \(h(x+y) \neq h(x)\). \\
